Dac summary 01/19/2021

### 2021-11-13 final_dac_summary_pull_20210119.Rmd
prelim analyses

This script goes through data that has been returned from the DAC on 1/19 and summarizes it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

#------
### add a column to the original dataframe with a 0 if not in any group, -1 if healthy, and 1 if depressed
data_empi_acc_f_phq$depGroupVar = 0
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_depressed_group)] = 1
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_healthy_group)] = -1
data_empi_acc_f_phq$depGroupVar = ordered(data_empi_acc_f_phq$depGroupVar)

@@

##########################################################
#   Step 8 - Regressions in dep/non dep                  #
##########################################################
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

@@

@@

@@

@@

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)
```

@@

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)
```

@@

>>>>

This script goes through data that has been returned from the DAC on 1/19 and summarizes it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

@@

##########################################################
#                Step 8 - Regressions                    #
##########################################################

```{r dep_vs_healthy_regressions}

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

@@

#visreg
sapply(fascicle_lm, visreg)
```

@@

#visreg
#sapply(fascicle_lm, visreg)
```
```{r phq2_correlation_fascicles_dep}
#isolate out only the depressed group and healthy group
dep_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar == 1,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq2_dep <- dep_groups_for_ICD_analysis %>% filter(!is.na(PHQ.2) & PHQ.2 != 0) %>% filter(depGroupVar == 1)

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.2, list(i = as.name(x))), data = with_phq2_dep)
})
names(fascicle_lm) <- fascicle_names

@@

#visreg
#sapply(fascicle_lm, visreg)
```
```{r phq9_correlation_fascicles_dep}
#isolate out only the depressed group and healthy group
dep_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar == 1,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq9_dep <- dep_groups_for_ICD_analysis %>% filter(!is.na(PHQ.9) & PHQ.9 != 0)

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9_dep)
})
names(fascicle_lm) <- fascicle_names

@@

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#### age histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$PAT_AGE_AT_EXAM,
main = paste0("Age In Good Mimosa Group : n = ", dim(dep_and_healthy_groups_for_ICD_analysis)[1]), xlab = "Age", breaks = 10)

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_age_lm,visreg)
```

@@

#### sex histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_sex_lm,visreg)
```

@@

```
```{r age_by_depression_fascicles}
#sex by depression
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthhy = 713, total n = 1106

#lm
fascicle_agedep_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_agedep_lm) <- fascicle_names

#anova
fascicle_agedep_anova <- lapply(fascicle_agedep_lm, anova)

#fdr corrected
fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 3)
print(fascicle_agedep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)
